### 2015-07-11 narrative/qos.tex
finished qos.

\subsubsection{Quality of Service (QoS)}
Our ultimate goal, rather than just performance predictability, is to offer
predictable QoS for the storage system.
%Performance quality can be expressed in either relative or absolute
%terms. Examples of relative performance terms are ``fair'',
%``proportional'', or ``priority/class-based'' (``the higher the
%priority the better the service'' or ``1st class is better than
%2nd''). The key advantage of relative performance terms is that
%they are easy to implement. The key disadvantage is the difficulty
%of making any guarantees based on those implementations --
%even relative guarantees are mired by the well-known effect of
%priority inversion~\cite{lampson:cacm80}. Examples of absolute
%performance terms are ``rate-based'', ``soft real-time'', and
%``hard real-time''. The key advantage of absolute performance
%terms are that they enable the implementation of strong
%guarantees: absolute terms enable agreements between application
%tasks and storage that we call \emph{reservations} and that do not
%change meaning depending
%on the storage system's workload. The key challenge of absolute
%performance terms is that their implementation is non-trivial,
%especially in large-scale systems.
One of the key differentiating features this project offers is driving storage
decisions through QoS~\emph{reservations} rather than continuing the current
model of allowing applications to compete freely without restriction for part
or all of the storage resources. The current approach leads to interference
effects~\cite{lofstead:2010:io-variability,liu_hotstorage} that can greatly
impact I/O performance predictability. 
%Further, with the introduction of additional tiers in the
%storage stack, the performance variability will increase with greater
%competiion for limited high performance resources. 
%% Temporaily commented out the above sentence, because it may not be true for
%the next DOE systems. 
Unfettered, this competition can yield lower system and application performance
than if applications attempt to reserve storage resources thereby enabling the
storage system to reason over its performance in terms of reservations and
actual performance.  In the cases where an application arrives that needs to
run more urgently than any of the other already running applications, the
system can rapidly respond to it by reducing the amount of resources taken by
less urgent applications, allowing the urgent application to finish, and later
reverting back to the previous committed resource level for the rest.  This can
be automatically enforced via user- or administrator- specified
\textit{policies}\S\ref{sec:data-description}.

@@

\paragraph{Challenges:}
The deep and heterogeneous memory and storage hierarchy we are assuming for
this proposal complicates the relationship between workload-dependent and
workload-independent metrics: the performance of a task can significantly
differ depending on what levels of the hierarchy are involved. Furthermore, an
important goal of the proposed project is to enable applications to reason
about the trade-off between resolution and latency, adding yet another
dimension to how tasks are mapped to resources.

@@

\item To offer latency/latency trade-offs, the system must be able
to quickly generate a number of data production plans, involving
different parts of the hierarchy and different data resolutions.
It will then use the utilization model to estimate the latency for
each production plan and the resolutions they can provide. Here
again, pseudo-random selection could reduce the number of resources
that would be involved, thereby increasing scalability.

>>>>

\subsubsection{Quality of Service (QoS)}
Our ultimate goal, rather than just performance predictability, is to offer
predictable QoS for the storage system.
%Performance quality can be expressed in either relative or absolute
%terms. Examples of relative performance terms are ``fair'',
%``proportional'', or ``priority/class-based'' (``the higher the
%priority the better the service'' or ``1st class is better than
%2nd''). The key advantage of relative performance terms is that
%they are easy to implement. The key disadvantage is the difficulty
%of making any guarantees based on those implementations --
%even relative guarantees are mired by the well-known effect of
%priority inversion~\cite{lampson:cacm80}. Examples of absolute
%performance terms are ``rate-based'', ``soft real-time'', and
%``hard real-time''. The key advantage of absolute performance
%terms are that they enable the implementation of strong
%guarantees: absolute terms enable agreements between application
%tasks and storage that we call \emph{reservations} and that do not
%change meaning depending
%on the storage system's workload. The key challenge of absolute
%performance terms is that their implementation is non-trivial,
%especially in large-scale systems.
One of the key differentiating features this project offers is driving storage
decisions through QoS~\emph{reservations} rather than continuing the current
model of allowing applications to compete freely without restriction for part
or all of the storage resources. The current approach leads to interference
effects~\cite{lofstead:2010:io-variability,liu_hotstorage} that can greatly
impact I/O performance predictability. 
%Further, with the introduction of additional tiers in the
%storage stack, the performance variability will increase with greater
%competiion for limited high performance resources. 
%% Temporaily commented out the above sentence, because it may not be true for
%the next DOE systems. 
Unfettered, this competition can yield lower system and application performance
than if applications attempt to reserve storage resources thereby enabling the
storage system to reason over its performance in terms of reservations and
actual performance.  In the cases where an application arrives that needs to
run more urgently than any of the other already running applications, the
system can rapidly respond to it by reducing the amount of resources taken by
less urgent applications, allowing the urgent application to finish, and later
reverting back to the previous committed resource level for the rest.  This can
be automatically enforced via user- or administrator- specified
policies.

@@

\paragraph{Challenges:}
The deep and heterogeneous memory and storage hierarchy we are assuming for
this proposal complicates the relationship between workload-dependent and
workload-independent metrics: the performance of a task can significantly
differ depending on what levels of the hierarchy are involved. Furthermore, an
important goal of the proposed project is to enable applications to reason
about the trade-off between accuracy and performance, adding yet another
dimension to how tasks are mapped to resources.

@@

\item To offer performance and accuracy trade-offs, the system must be able
to quickly generate a number of data production plans, involving
different parts of the hierarchy and different data accuracy.
It will then use the utilization model to estimate the performance for
each production plan and the accuracy they can provide. Here
again, pseudo-random selection could reduce the number of resources
that would be involved, thereby increasing scalability.
